artData

### 2018-02-07 docs/articles/dataMaid_artData.Rmd
Updated webpage + added "Courses" tab

---
dataMaid: yes
title: artData
subtitle: "Autogenerated data summary from dataMaid"
date: 2018-01-12 19:32:44
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
```{r visualFunctions, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:

@@

------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                 character   factor    labelled   numeric   integer   logical    Date   
----------------------------------------------------- ----------- --------- ---------- --------- --------- --------- ---------
Identify miscoded missing values                        &times;    &times;   &times;    &times;   &times;

@@

"Francisco Goya", "Francisco de Zurbaran", "Francois Boucher", 

@@

"Georges Braque", "Georges Seurat", "Georges de la Tour", "Georgia O'Keeffe", 

@@

"Jan Matsys", "Jan Vermeer", "Jan van Eyck", "Jasper Johns, Jr.", 

@@

@@

1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 

@@

</div>
<div class = "col-lg-4">
```{r Var-6-Location, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:97, .Label = c("Alfred Stieglitz Collection, Carl Van Vechten Gallery", 
"Alte Nationalgalerie", "Alte Pinakothek", "Art Institute of Chicago", 
"Brancacci Chapel", "Centre Pompidou", "Christie's Auction House", 
"Cleveland Museum of Art", "Courtauld Institute of Art, University of London", 
"Detroit Institute of Arts", "Fogg Museum", "Forberg Collection, Albertina", 
"Freer Gallery of Art", "Galleria dell'Accademia Carrara", "Gallerie dell'Accademia", 
"Gemaeldegalerie Alte Meister", "Gemaldegalerie", "Gemaldegalerie Alte Meister", 
"Gemeentemuseum Den Haag", "Guggenheim Museum", "Hamburger Kunsthalle", 
"Harvard Art Museum", "Hermitage Museum", "Hill-Stead Museum", 
"Kroller-Muller Museum", "Kunsthalle (Museum of Art)", "Kunsthaus Zurich", 
"Kunsthistorisches Museum", "Kunstmuseum Basel", "Kunstsammlung Nordrhein-Westfalen", 
"Kunthistorisches Museum", "Lenbach House State Gallery", "Leopold Hoesch Museum", 
"Louvre Museum", "Manchester Art Gallery", "Mauritshuis", "Medici Riccardi Palace", 
"Memlingmuseum, Sint-Janshospitaal", "Menard Art Museum", "Metropolitan Museum of Art", 
"Mr. and Mrs. Leigh B. Block", "Musee National d'Art Moderne", 
"Musee Royaux des Beaux-Arts", "Musee d'Orsay", "Musee d'Unterlinden", 
"Musee des Beaux-Arts de Nantes", "Museo Civico", "Museo Reina Sofia", 
"Museo del Novecento", "Museo del Prado", "Museum Folkwant", 
"Museum Gemaldegalerie der Staatlichen Museen", "Museum Ludwig", 
"Museum of Contemporary Art", "Museum of Fine Arts", "Museum of Modern Art", 
"National Gallery", "National Gallery of Art", "National Gallery of Scotland", 
"National Gallery, Galleria degli Uffizi, Louvre Museum", "Nationalgalerie, Staatliche Museen", 
"Nationalgalerie, Staatliche Museen zu Berlin", "Neue Pinakothe", 
"New Pinakothek", "Norton Simon Museum", "Osterreichische Galerie Belvedere", 
"Palazzo Ducale", "Peggy Guggenheim Collection", "Pennsylvania Academy of the Fine Arts", 
"Philadelphia Museum of Art", "Phillips Collections", "Pompidou Centre", 
"Private Collection", "Rijksmuseum", "Royal Collection, Windsor Castle", 
"Royal Museums of Fine Arts of Beligum", "Samuel H. Kress Collection, National Gallery of Art", 
"San Francisco Museum of Modern Art", "Santo Tome", "Scrovegni Chapel", 
"Staatliche Museen", "Stadtische Galerie im Lenbachhaus", "State Russian Museum", 
"Stedelijk Museum", "Szepmuveszeti Muzeum", "Tate Britain", "The Frick Collection", 
"Toledo Museum of Art", "Trustees of the Grosvenor Estate", "Uffizi Gallery", 
"Victoria & Albert Museum", "Villa Coredellina", "Wallraf-Richartz Museum", 
"Walters Art Museum", "Whitney Museum of American Art", "Wildenstein Collection", 
"von Zezschwitz (for sale)"), class = "factor"), y = c(1L, 1L, 
2L, 8L, 1L, 1L, 1L, 2L, 1L, 2L, 1L, 1L, 1L, 1L, 1L, 1L, 4L, 2L, 
1L, 1L, 4L, 1L, 1L, 1L, 1L, 2L, 3L, 4L, 6L, 3L, 4L, 2L, 1L, 12L, 
1L, 1L, 1L, 1L, 1L, 4L, 1L, 2L, 1L, 2L, 1L, 1L, 1L, 1L, 1L, 7L, 
1L, 1L, 2L, 1L, 1L, 8L, 13L, 6L, 3L, 1L, 1L, 1L, 4L, 1L, 1L, 
1L, 1L, 6L, 1L, 1L, 1L, 1L, 2L, 2L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 
1L, 2L, 1L, 1L, 4L, 1L, 1L, 1L, 1L, 1L, 1L, 3L, 1L, 1L, 1L, 1L
)), .Names = c("x", "y"), row.names = c(NA, -97L), class = "data.frame"), 
    vnam = "Location")
```
</div>
</div>

@@

</div>
<div class = "col-lg-4">
```{r Var-10-Media, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:27, .Label = c("acrylic paint", 
"aquatint, etching", "collage", "collage, oil paint", "egg tempera", 
"enamel", "encaustic, oil paint, and collage on fabric", "fresco", 
"gouache and graphite", "gouache-painted paper", "ink and color", 
"ink, color, gold and silver", "oil and metallic paint", "oil paint", 
"oil paint and charcoal", "oil paint and collage", "oil paint and magna", 
"oil paint and pastel", "oil paint, tempera, pastel", "oil piant", 
"pastel", "screen photography, transparent paint, silkscreen", 
"tempera", "varnished tempera", "watercolor", "watercolor, pen and ink", 
"wood cut"), class = "factor"), y = c(2L, 1L, 1L, 1L, 2L, 1L, 
1L, 4L, 1L, 1L, 1L, 1L, 1L, 147L, 2L, 1L, 1L, 1L, 1L, 2L, 1L, 
1L, 9L, 1L, 2L, 1L, 2L)), .Names = c("x", "y"), row.names = c(NA, 
-27L), class = "data.frame"), vnam = "Media")
```
</div>
</div>

- Note that the following levels have at most five observations: \"acrylic paint\", \"aquatint, etching\", \"collage\", \"collage, oil paint\", \"egg tempera\", \"enamel\", \"encaustic, oil paint, and collage on fabric\", \"fresco\", \"gouache and graphite\", \"gouache-painted paper\" (15 additional values omitted).

@@

</div>
<div class = "col-lg-4">
```{r Var-11-Movement, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:85, .Label = c("Abstract Artist", 
"Abstract Expressionist", "Abstract Expressionist:Color Field", 
"Abstract Expressionist:Neo-Dada:Pop Art", "American Modernist", 
"American Realist", "Analytic Cubist", "Baroque", "Bauhaus", 
"British Expressionist", "Classicist:Baroque", "Constructivist", 
"Cubism", "Cubist", "Dada", "Dada:New Objectivity", "Dada:Surrealist", 
"De Stijl", "Dutch Golden Age", "Dutch Golden Age:Baroque", "Dutch and Flemish Renaissance", 
"Early Netherlandish", "Early Netherlandish Renaissance", "Early Renaissance", 
"English Romantic", "Expressionist", "Expressionist:Abstract Artist", 
"Expressionist:Bauhaus:Surrealist", "Expressionist:Surrealist", 
"Fauvist", "Flemish", "French Baroque", "French Impressionist", 
"Futurism", "Geometric abstraction", "German Expressionist", 
"German Realist", "German Renaissance", "German Romantic", "High Renaissance", 
"High Renaissance:Mannerist", "Impressionist", "Impressionist:Expressionist", 
"Italian Modernist", "Italian Renaissance", "Late Gothic", "Mannerist", 
"Mechanistic Cubist", "Merz", "Neo-Expressionist", "Neo-Impresionist:Divisionist:Fauvist:Cubist", 
"Neoclassicist", "Neue Sachlichkeit", "Northern Renaissance", 
"Orphist", "Orphist:Cubist:Expressionist", "Pop Artist", "Post-Impressionist", 
"Post-Impressionist:Neo-Impressionist:Pointillist", "Pre-Raphaelite", 
"Realism", "Realist", "Realist:Impressionist", "Realist:Surrealist:Pop Artist", 
"Regionalist", "Renaissance", "Rimpa school", "Rococo", "Rococo:Neoclassicist", 
"Romantic", "Russian Expressionist", "Russian Symbolist", "Scottish landscape painter", 
"Sienese school:Gothic style", "Social Realism", "Spatialist", 
"Suprematist", "Surrealism", "Surrealism:Dada", "Surrealist", 
"Surrealist:Expressionist", "Surrealist:Expressionist:Cubist:Formalist", 
"Symbolist", "Tonalist", "Video Artist:Installation:Happening:Fluxus"
), class = "factor"), y = c(1L, 5L, 1L, 1L, 1L, 1L, 1L, 14L, 
1L, 1L, 2L, 1L, 4L, 2L, 1L, 1L, 3L, 1L, 1L, 4L, 3L, 1L, 2L, 2L, 
1L, 11L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 2L, 1L, 1L, 3L, 3L, 3L, 
6L, 1L, 4L, 1L, 1L, 8L, 2L, 3L, 1L, 1L, 1L, 1L, 2L, 1L, 7L, 1L, 
1L, 1L, 6L, 1L, 2L, 1L, 5L, 1L, 1L, 1L, 2L, 1L, 2L, 1L, 9L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 1L, 3L, 1L, 1L)), .Names = c("x", 
"y"), row.names = c(NA, -85L), class = "data.frame"), vnam = "Movement")
```
</div>
</div>

@@

 *  Created by Claus Thorn Ekstrøm.

 *  Report creation time: Fri Jan 12 2018 19:32:44

 *  dataMaid v1.0.1 [Pkg: 2017-11-13 from local (ekstroem/dataMaid@NA)]

 *  R version 3.4.3 (2017-11-30).

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS High Sierra 10.13.2).

>>>>

---
dataMaid: yes
title: artData
subtitle: "Autogenerated data summary from dataMaid"
date: 2018-02-07 18:03:36
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
```{r visualFunctions, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:

@@

------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                 character   factor    labelled   numeric   integer   logical    Date   
----------------------------------------------------- ----------- --------- ---------- --------- --------- --------- ---------
Identify miscoded missing values                        &times;    &times;   &times;    &times;   &times;             &times;

@@

"Francisco de Zurbaran", "Francisco Goya", "Francois Boucher", 

@@

"Georges Braque", "Georges de la Tour", "Georges Seurat", "Georgia O'Keeffe", 

@@

"Jan Matsys", "Jan van Eyck", "Jan Vermeer", "Jasper Johns, Jr.", 

@@

1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 

@@

1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 1L, 1L, 1L, 

@@

</div>
<div class = "col-lg-4">
```{r Var-6-Location, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:97, .Label = c("Alfred Stieglitz Collection, Carl Van Vechten Gallery", 
"Alte Nationalgalerie", "Alte Pinakothek", "Art Institute of Chicago", 
"Brancacci Chapel", "Centre Pompidou", "Christie's Auction House", 
"Cleveland Museum of Art", "Courtauld Institute of Art, University of London", 
"Detroit Institute of Arts", "Fogg Museum", "Forberg Collection, Albertina", 
"Freer Gallery of Art", "Galleria dell'Accademia Carrara", "Gallerie dell'Accademia", 
"Gemaeldegalerie Alte Meister", "Gemaldegalerie", "Gemaldegalerie Alte Meister", 
"Gemeentemuseum Den Haag", "Guggenheim Museum", "Hamburger Kunsthalle", 
"Harvard Art Museum", "Hermitage Museum", "Hill-Stead Museum", 
"Kroller-Muller Museum", "Kunsthalle (Museum of Art)", "Kunsthaus Zurich", 
"Kunsthistorisches Museum", "Kunstmuseum Basel", "Kunstsammlung Nordrhein-Westfalen", 
"Kunthistorisches Museum", "Lenbach House State Gallery", "Leopold Hoesch Museum", 
"Louvre Museum", "Manchester Art Gallery", "Mauritshuis", "Medici Riccardi Palace", 
"Memlingmuseum, Sint-Janshospitaal", "Menard Art Museum", "Metropolitan Museum of Art", 
"Mr. and Mrs. Leigh B. Block", "Musee d'Orsay", "Musee d'Unterlinden", 
"Musee des Beaux-Arts de Nantes", "Musee National d'Art Moderne", 
"Musee Royaux des Beaux-Arts", "Museo Civico", "Museo del Novecento", 
"Museo del Prado", "Museo Reina Sofia", "Museum Folkwant", "Museum Gemaldegalerie der Staatlichen Museen", 
"Museum Ludwig", "Museum of Contemporary Art", "Museum of Fine Arts", 
"Museum of Modern Art", "National Gallery", "National Gallery of Art", 
"National Gallery of Scotland", "National Gallery, Galleria degli Uffizi, Louvre Museum", 
"Nationalgalerie, Staatliche Museen", "Nationalgalerie, Staatliche Museen zu Berlin", 
"Neue Pinakothe", "New Pinakothek", "Norton Simon Museum", "Osterreichische Galerie Belvedere", 
"Palazzo Ducale", "Peggy Guggenheim Collection", "Pennsylvania Academy of the Fine Arts", 
"Philadelphia Museum of Art", "Phillips Collections", "Pompidou Centre", 
"Private Collection", "Rijksmuseum", "Royal Collection, Windsor Castle", 
"Royal Museums of Fine Arts of Beligum", "Samuel H. Kress Collection, National Gallery of Art", 
"San Francisco Museum of Modern Art", "Santo Tome", "Scrovegni Chapel", 
"Stadtische Galerie im Lenbachhaus", "State Russian Museum", 
"Stedelijk Museum", "Staatliche Museen", "Szepmuveszeti Muzeum", 
"Tate Britain", "The Frick Collection", "Toledo Museum of Art", 
"Trustees of the Grosvenor Estate", "Uffizi Gallery", "Victoria & Albert Museum", 
"Villa Coredellina", "von Zezschwitz (for sale)", "Wallraf-Richartz Museum", 
"Walters Art Museum", "Whitney Museum of American Art", "Wildenstein Collection"
), class = "factor"), y = c(1L, 1L, 2L, 8L, 1L, 1L, 1L, 2L, 1L, 
2L, 1L, 1L, 1L, 1L, 1L, 1L, 4L, 2L, 1L, 1L, 4L, 1L, 1L, 1L, 1L, 
2L, 3L, 4L, 6L, 3L, 4L, 2L, 1L, 12L, 1L, 1L, 1L, 1L, 1L, 4L, 
1L, 2L, 1L, 1L, 2L, 1L, 1L, 1L, 7L, 1L, 1L, 1L, 2L, 1L, 1L, 8L, 
13L, 6L, 3L, 1L, 1L, 1L, 4L, 1L, 1L, 1L, 1L, 6L, 1L, 1L, 1L, 
1L, 2L, 2L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 2L, 1L, 4L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 3L, 1L, 1L, 1L)), .Names = c("x", "y"
), row.names = c(NA, -97L), class = "data.frame"), vnam = "Location")
```
</div>
</div>

@@

</div>
<div class = "col-lg-4">
```{r Var-10-Media, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:27, .Label = c("acrylic paint", 
"aquatint, etching", "collage", "collage, oil paint", "egg tempera", 
"enamel", "encaustic, oil paint, and collage on fabric", "fresco", 
"gouache-painted paper", "gouache and graphite", "ink and color", 
"ink, color, gold and silver", "oil and metallic paint", "oil paint", 
"oil paint and charcoal", "oil paint and collage", "oil paint and magna", 
"oil paint and pastel", "oil paint, tempera, pastel", "oil piant", 
"pastel", "screen photography, transparent paint, silkscreen", 
"tempera", "varnished tempera", "watercolor", "watercolor, pen and ink", 
"wood cut"), class = "factor"), y = c(2L, 1L, 1L, 1L, 2L, 1L, 
1L, 4L, 1L, 1L, 1L, 1L, 1L, 147L, 2L, 1L, 1L, 1L, 1L, 2L, 1L, 
1L, 9L, 1L, 2L, 1L, 2L)), .Names = c("x", "y"), row.names = c(NA, 
-27L), class = "data.frame"), vnam = "Media")
```
</div>
</div>

- Note that the following levels have at most five observations: \"acrylic paint\", \"aquatint, etching\", \"collage\", \"collage, oil paint\", \"egg tempera\", \"enamel\", \"encaustic, oil paint, and collage on fabric\", \"fresco\", \"gouache-painted paper\", \"gouache and graphite\" (15 additional values omitted).

@@

</div>
<div class = "col-lg-4">
```{r Var-11-Movement, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:85, .Label = c("Abstract Artist", 
"Abstract Expressionist", "Abstract Expressionist:Color Field", 
"Abstract Expressionist:Neo-Dada:Pop Art", "American Modernist", 
"American Realist", "Analytic Cubist", "Baroque", "Bauhaus", 
"British Expressionist", "Classicist:Baroque", "Constructivist", 
"Cubism", "Cubist", "Dada", "Dada:New Objectivity", "Dada:Surrealist", 
"De Stijl", "Dutch and Flemish Renaissance", "Dutch Golden Age", 
"Dutch Golden Age:Baroque", "Early Netherlandish", "Early Netherlandish Renaissance", 
"Early Renaissance", "English Romantic", "Expressionist", "Expressionist:Abstract Artist", 
"Expressionist:Bauhaus:Surrealist", "Expressionist:Surrealist", 
"Fauvist", "Flemish", "French Baroque", "French Impressionist", 
"Futurism", "Geometric abstraction", "German Expressionist", 
"German Realist", "German Renaissance", "German Romantic", "High Renaissance", 
"High Renaissance:Mannerist", "Impressionist", "Impressionist:Expressionist", 
"Italian Modernist", "Italian Renaissance", "Late Gothic", "Mannerist", 
"Mechanistic Cubist", "Merz", "Neo-Expressionist", "Neo-Impresionist:Divisionist:Fauvist:Cubist", 
"Neoclassicist", "Neue Sachlichkeit", "Northern Renaissance", 
"Orphist", "Orphist:Cubist:Expressionist", "Pop Artist", "Post-Impressionist", 
"Post-Impressionist:Neo-Impressionist:Pointillist", "Pre-Raphaelite", 
"Realism", "Realist", "Realist:Impressionist", "Realist:Surrealist:Pop Artist", 
"Regionalist", "Renaissance", "Rimpa school", "Rococo", "Rococo:Neoclassicist", 
"Romantic", "Russian Expressionist", "Russian Symbolist", "Scottish landscape painter", 
"Sienese school:Gothic style", "Social Realism", "Spatialist", 
"Suprematist", "Surrealism", "Surrealism:Dada", "Surrealist", 
"Surrealist:Expressionist", "Surrealist:Expressionist:Cubist:Formalist", 
"Symbolist", "Tonalist", "Video Artist:Installation:Happening:Fluxus"
), class = "factor"), y = c(1L, 5L, 1L, 1L, 1L, 1L, 1L, 14L, 
1L, 1L, 2L, 1L, 4L, 2L, 1L, 1L, 3L, 1L, 3L, 1L, 4L, 1L, 2L, 2L, 
1L, 11L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 2L, 1L, 1L, 3L, 3L, 3L, 
6L, 1L, 4L, 1L, 1L, 8L, 2L, 3L, 1L, 1L, 1L, 1L, 2L, 1L, 7L, 1L, 
1L, 1L, 6L, 1L, 2L, 1L, 5L, 1L, 1L, 1L, 2L, 1L, 2L, 1L, 9L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 1L, 1L, 3L, 1L, 1L)), .Names = c("x", 
"y"), row.names = c(NA, -85L), class = "data.frame"), vnam = "Movement")
```
</div>
</div>

@@

 *  Created by Anne Helby Petersen.

 *  Report creation time: on feb 07 2018 18:04:14

 *  dataMaid v1.1.0 [Pkg: 2018-02-03 from local (ekstroem/dataMaid@NA)]

 *  R version 3.4.2 (2017-09-28).

 *  Platform: x86_64-w64-mingw32/x64 (64-bit)(Windows 7 x64 (build 7601) Service Pack 1).
